Cosmic web alignments with the shape, angular momentum and peculiar velocities of dark matter halos

### 2014-02-06 paper/main.tex
starting to write the conclusions

\title[Cosmic web alignments with halos]{Cosmic web alignments with the shape, angular momentum and peculiar velocities of dark matter halos}  
\author[S. Contreras et al.]{
\parbox[t]{\textwidth}{\raggedright 
  Jaime E. Forero-Romero$^{1}$,
  Sergio Contreras$^{2}$,
  Nelson Padilla$^{2}$ 
}
\vspace*{6pt}\\
$^{1}$Uni A
$^{2}$Uni B
}
\maketitle

@@

&   & & 
wall & - & $>10^{12}$\hMsun\\\hline

@@

& &  $2.1$ &
wall & $++$ & stronger $>10^{12}$\hMsun\\\hline \hline

@@

\begin{figure*}
\includegraphics[width=0.9\textwidth]{Fig0.pdf}
\caption{Fraction of halos in a mass bin that show a preferential
  alignment with respect to an eigenvector for the three properties
  studies in this paper: shape (major axis), angular momentum and
  peculiar velocity. Left column presents the results against the Tweb
  and the right the Vweb. Strong colors refer to $256^3$ grid
  resolutions and lighter colors to a $512^3$ grid. The thick black
  horizontal line at $0.33$ corresponds to the expected fraction for a
  a random vector field.
\label{fig:preferential}}
\end{figure*}

@@

@@

>>>>

\title[Cosmic web alignments with halos]{Cosmic web alignments with the shape, angular momentum and peculiar velocities of dark matter halos}  
\author[J.E. Forero-Romero et al.]{
\parbox[t]{\textwidth}{\raggedright 
  Jaime E. Forero-Romero$^{1}$,
  Sergio Contreras$^{2}$,
  Nelson Padilla$^{2}$ 
}
\vspace*{6pt}\\
$^{1}$Uni A
$^{2}$Uni B
}
\maketitle

@@

&   & & 
wall & none & $>10^{12}$\hMsun\\\hline

@@

& & &
wall& $+$ & $<10^{12}$\hMsun\\
& &    &
wall & $++$ & $>10^{12}$\hMsun\\\hline \hline

@@

\begin{figure*}
\includegraphics[width=0.8\textwidth]{Fig0.pdf}
\caption{Fraction of halos in a mass bin that show a preferential
  alignment with respect to an eigenvector for the three properties
  studies in this paper: shape (major axis), angular momentum and
  peculiar velocity. Left column presents the results against the Vweb
  and the right the Tweb. Strong colors refer to $256^3$ grid
  resolutions and lighter colors to a $512^3$ grid. The thick black
  horizontal line at $0.33$ corresponds to the expected fraction for a
  a random vector field.
\label{fig:preferential}}
\end{figure*}

@@

The peculiar velocities show a weak but consistent alignment along the
third eigenvector $\vec{e}_{3}$ of the Tweb for all masses below
$10^{13.0}$\hMsun-$10^{13.5}$\hMsun depending on the grid
resolution. $45\%$ of the halos are aligned while only $25\%$ are
aligned along the first eigenvector $\vec{e}_1$. This suggests that
halos tend to move along filaments and parallel to the walls, except
at higher masses where the alignments get randomized.  In contrast,
the peculiar velocities with respect to the Vweb do not show any clear
alignment trend.

@@

We have examined the alignment of shape, angular momentum and peculiar
velocity of dark matter halos with respect to the cosmic
web. We use publicly available data from two algorithms
implemented on a large cosmological N-body simulation to study halo
populations spanning five orders of magnitude in mass. The first
algorithm uses the tidal field and the second the velocity shear, both
present local results on scales of $0.5$\hMpc to $1.0$\hMpc.
